Title

### 2013-01-31 inc/gun/gun_design.tex
added anode and cathode pictures

@@

These requirements lead to the fabrication of cathode/Wehnelt and anode pair based on the design of Togawa \textit{et al.} \cite{togawa_ceb6_2007}.
A schematic of this design, overlayed by a Finite Element Model (FEM) simulation of the electic field, is shown in \ref{fig:gun-field}.
The schematic shows that the aperture concerns are easily satisfied.
From the field equipotentials, it is clear that this design has a consistently flat electric field for large displacements off the central axis.

>>>>

\begin{figure}
  \centering
  \centerline{\includegraphics{cathode.jpg} \includegraphics{anode.jpg}}
  \caption{
    Pictured are the cathode (left) and anode (right) of the accelerator built at UIC from a design by Togawa \protect\textit{et al.} \protect\cite{togawa_ceb6_2007}.
    The photocathode is visible in the cathode Wehnelt aperture.
    The anode is viewed as installed in the column, through the opened port normally occupied by the cathode and high voltage feedthrough.
    The white material seen in both images helps to prevent electrical arcing under high voltage.
  }
  \label{fig:togawa-pic}
\end{figure}

These requirements lead to the fabrication of cathode/Wehnelt and anode pair based on the design of Togawa \textit{et al.} \cite{togawa_ceb6_2007} (pictured in \ref{fig:togawa-pic}).
A schematic of this design, overlayed by a Finite Element Model (FEM) simulation of the electic field, is shown in \ref{fig:gun-field}.
The schematic shows that the aperture concerns are easily satisfied.
From the field equipotentials, it is clear that this design has a consistently flat electric field for large displacements off the central axis.

@@
